### 2017-04-13 paper/oopsla17-submission/intro2.tex

\mypara{Localizing Errors}
%
Several recent papers have proposed ways
to improve feedback via error \emph{localization}.
%
At a high-level these techniques analyze
the set of typing constraints to find
the minimum (weighted) subset that,
if removed would make the constraints
satisfiable and hence, memory-safe~\citep{Jose:2011}
or well-typed~\citep{Zhang2014-lv,Loncaric2016-uk,Chen2014-gd,Pavlinovic2014-mr}.
The finger of blame is then pointed at the
sub-terms that yielded those constraints.

This minimum-weight approach suffers
from several drawbacks.
%
First, they are not \emph{extensible}:
% the weights and analyses are limited
% to attributes of the constraints, and
% not other \emph{signals} from the
% program's syntax that may be more
% germane to error localization. Furthermore,
the constraint languages and algorithms for computing
the minimum weighted subset must be
designed afresh for different kinds
of type systems and constraints \citep{Loncaric2016-uk}.
%
Second, and perhaps most importantly,
they are not \emph{adaptable}: the
weights are fixed in an ad-hoc fashion, based on the
\emph{analysis designer's} notion
of what kinds of errors are more
or less likely, rather than
capturing and adapting to the
ground truth about the kinds
of errors programmers actually
make in practice.

@@

Our \emph{first contribution} (\autoref{sec:overview})
is a set of more than 4,500 labeled programs,
gives us an accurate ground truth of
the kinds of errors and the (locations
of the) fixes that novices make in
practice.
%
We obtain this set by observing that
software development is an iterative
process; programmers eventually
fix their own ill-typed programs,
perhaps after multiple incorrect
exploratory attempts.
%
To exploit this observation we instrumented
the \ocaml compiler to collect fine-grained
traces of student interactions over two instances
of an undergraduate Programming Languages course at
%
\begin{anonsuppress}
UC San Diego (IRB \#140608).
\end{anonsuppress}
\begin{noanonsuppress}
AUTHOR's INSTITUTION (IRB HIDDEN).
\end{noanonsuppress}
%
We then post-process the resulting time-series
of programs submitted to the \ocaml compiler into
a set of pairs of ill-typed programs and their
subsequent \emph{fixes}, the first (type-)correct
program in the trace suffix.
%
Finally, we label the changed locations by computing a
\emph{tree-diff} between the two terms to find
the exact sub-terms that were changed in the fix.

>>>>

\mypara{Localizing Errors}
%
Several recent papers have proposed ways
to improve feedback via error \emph{localization}.
%
At a high-level these techniques analyze
the set of typing constraints to find
the minimum (weighted) subset that,
if removed would make the constraints
satisfiable and hence, memory-safe~\citep{Jose:2011}
or well-typed~\citep{Zhang2014-lv,Loncaric2016-uk,Chen2014-gd,Pavlinovic2014-mr}.
The finger of blame is then pointed at the
sub-terms that yielded those constraints.
%
This minimum-weight approach suffers
from two drawbacks.
%
First, they are not \emph{extensible}:
% the weights and analyses are limited
% to attributes of the constraints, and
% not other \emph{signals} from the
% program's syntax that may be more
% germane to error localization. Furthermore,
the constraint languages and algorithms for computing
the minimum weighted subset must be
designed afresh for different kinds
of type systems and constraints \citep{Loncaric2016-uk}.
%
Second, and perhaps most importantly,
they are not \emph{adaptable}: the
weights are fixed in an ad-hoc fashion, based on the
\emph{analysis designer's} notion
of what kinds of errors are more
or less likely, rather than
adapting to the kinds of mistakes
programmers actually make in practice.

@@

Our \emph{first contribution} (\autoref{sec:overview})
is a set of more than 4,500 labeled programs,
gives us an accurate ground truth of
the kinds of errors and the (locations
of the) fixes that novices make in
practice.
%
We obtain this set by observing that
software development is an iterative
process; programmers eventually
fix their own ill-typed programs,
perhaps after multiple incorrect
exploratory attempts.
%
To exploit this observation we instrumented
the \ocaml compiler to collect fine-grained
traces of student interactions over two instances
of an undergraduate Programming Languages course
%
\footnote{
% \begin{anonsuppress}
% UC San Diego (IRB \#140608).
% \end{anonsuppress}
% \begin{noanonsuppress}
at AUTHOR's INSTITUTION (IRB HIDDEN).
% \end{noanonsuppress}
}
%
We then post-process the resulting time-series
of programs submitted to the \ocaml compiler into
a set of pairs of ill-typed programs and their
subsequent \emph{fixes}, the first (type-)correct
program in the trace suffix.
%
Finally, we label the changed locations by computing a
\emph{tree-diff} between the two terms to find
the exact sub-terms that were changed in the fix.
